---
title: "Provider Procedure Audit"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    toc_depth: 2
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(lubridate)
library(knitr)
library(kableExtra)
```

```{r load-data}
df <- read_csv("~/Documents/Procedure_Audit/procedures.csv")
```

---

# Data Overview

```{r overview}
tibble(
  Metric = c("Total Records", "Unique Providers", "Unique CSNs", "Date Range"),
  Value = c(
    nrow(df),
    n_distinct(df$resident_name),
    n_distinct(df$csn),
    paste(min(df$service_date, na.rm = TRUE), "to", max(df$service_date, na.rm = TRUE))
  )
) |>
  kable(col.names = c("", "")) |>
  kable_styling(full_width = FALSE)
```

---

# Provider Activity

## Procedures per Provider

```{r resident-summary}
df |>
  group_by(resident_name, `Last Name`, `First Name`, PGY, `Program/Type`, `UC/ED Rotation`) |>
  summarise(
    Procedures    = n(),
    Unique_Proc_Types = n_distinct(procedure_type),
    .groups = "drop"
  ) |>
  arrange(desc(Procedures)) |>
  select(
    Provider      = resident_name,
    PGY,
    Program       = `Program/Type`,
    Rotation      = `UC/ED Rotation`,
    Procedures,
    `Unique Types` = Unique_Proc_Types
  ) |>
  kable() |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))
```

## Procedures by PGY Level

```{r by-pgy}
df |>
  count(PGY, procedure_type) |>
  pivot_wider(names_from = procedure_type, values_from = n, values_fill = 0) |>
  arrange(PGY) |>
  kable(caption = "Procedure Counts by PGY Level") |>
  kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover")) |>
  scroll_box(width = "100%")
```

## Procedures by Rotation (ED vs. UC)

```{r by-rotation}
df |>
  count(`UC/ED Rotation`, procedure_type) |>
  pivot_wider(names_from = procedure_type, values_from = n, values_fill = 0) |>
  kable(caption = "Procedure Counts by Rotation Type") |>
  kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover")) |>
  scroll_box(width = "100%")
```

---

# Procedure Breakdown

## Procedures per Visit

```{r procs-per-csn}
csn_summary <- df |>
  count(csn, name = "n_procedures") |>
  count(n_procedures, name = "n_visits") |>
  mutate(
    `% of All Visits` = scales::percent(n_visits / sum(n_visits), accuracy = 0.1)
  )

multi_pct <- df |>
  count(csn) |>
  summarise(pct = scales::percent(mean(n >= 2), accuracy = 0.1)) |>
  pull(pct)

csn_summary |>
  kable(col.names = c("Procedures per Visit", "# of Visits", "% of All Visits")) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))
```

`r multi_pct` of visits included 2 or more procedures.

## Overall Frequency

```{r proc-frequency, fig.width=7, fig.height=4}
df |>
  count(procedure_type, sort = TRUE) |>
  ggplot(aes(x = n, y = fct_reorder(procedure_type, n))) +
  geom_col(fill = "#2E86AB") +
  labs(
    title = "Procedure Volume by Type",
    x     = "Count",
    y     = NULL
  ) +
  theme_minimal()
```

## Procedure Mix by PGY Level

```{r proc-by-pgy, fig.width=8, fig.height=5}
df |>
  count(PGY, procedure_type) |>
  ggplot(aes(x = n, y = fct_reorder(procedure_type, n), fill = PGY)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c(
    "PGY1" = "#A8D5E2",
    "PGY2" = "#2E86AB",
    "PGY3" = "#1B5E7B",
    "PGY4" = "#0D3349"
  )) +
  labs(
    title = "Procedure Type by PGY Level",
    x     = "Count",
    y     = NULL,
    fill  = "PGY"
  ) +
  theme_minimal()
```

---

# Patient & Case Context

## Age Distribution

```{r age-dist, fig.width=6, fig.height=4}
df |>
  ggplot(aes(x = age_years)) +
  geom_histogram(binwidth = 1, fill = "#2E86AB", color = "white") +
  labs(
    title = "Age Distribution of Patients",
    x     = "Age (Years)",
    y     = "Count"
  ) +
  theme_minimal()
```

## Chief Complaint

```{r chief-complaint}
df |>
  count(chief_complaint, sort = TRUE) |>
  mutate(Percent = scales::percent(n / sum(n), accuracy = 0.1)) |>
  kable(col.names = c("Chief Complaint", "Count", "% of Total")) |>
  kable_styling(full_width = FALSE)
```

## ICD-10 Major Group

```{r icd-group}
df |>
  count(icd10_major_group, sort = TRUE) |>
  mutate(Percent = scales::percent(n / sum(n), accuracy = 0.1)) |>
  kable(col.names = c("ICD-10 Group", "Count", "% of Total")) |>
  kable_styling(full_width = FALSE)
```

## Acuity (ESI)

```{r acuity, fig.width=5, fig.height=4}
df |>
  count(acuity_esi) |>
  mutate(acuity_esi = factor(acuity_esi)) |>
  ggplot(aes(x = acuity_esi, y = n)) +
  geom_col(fill = "#2E86AB") +
  labs(
    title = "ESI Acuity Distribution",
    x     = "ESI Level",
    y     = "Count"
  ) +
  theme_minimal()
```

## Disposition

```{r disposition}
df |>
  count(ed_general_disposition, sort = TRUE) |>
  mutate(Percent = scales::percent(n / sum(n), accuracy = 0.1)) |>
  kable(col.names = c("Disposition", "Count", "% of Total")) |>
  kable_styling(full_width = FALSE)
```

---

# Trends Over Time

```{r time-trends, fig.width=8, fig.height=4}
df |>
  mutate(month = floor_date(service_date, "month")) |>
  count(month) |>
  ggplot(aes(x = month, y = n)) +
  geom_line(color = "#2E86AB", linewidth = 1) +
  geom_point(color = "#2E86AB", size = 2) +
  labs(
    title = "Procedures Over Time",
    x     = NULL,
    y     = "Count"
  ) +
  theme_minimal()
```
